Add Plant Functional Type (PFT) labels

### 2021-04-05 R/add_plant_functional_type.Rmd
adam says zinnia is grass_herb
joining by individualID seems to work better than uid

growthForms <- vst_apparentindividual %>% 
  select(uid, growthForm)

# merge the growthForm column into the spectra data by uid 
cleaned_spectra_merged <- merge(cleaned_spectra, growthForms, by = "uid", all.x=TRUE)

@@

# summarize the merged growthform data

@@

  else if(genusSpecies == "Zinnia acerosa"){
    taxon_pft_lookup$pft[i] = "???" # forb/herb, subshrub - grass_herb?
    taxon_pft_lookup$commonName[i] = "desert zinnia"}

>>>>

growthForms <- vst_apparentindividual %>% 
  select(individualID, growthForm)

# merge the growthForm column into the spectra data
cleaned_spectra_merged <- right_join(cleaned_spectra, growthForms, by = "individualID")

@@

# summarize the merged growthform data
cleaned_spectra_merged %>% 
  distinct(spectraID, .keep_all = TRUE) %>% 
  group_by(growthForm) %>% 
    tally() 
```

@@

  else if(genusSpecies == "Zinnia acerosa"){
    taxon_pft_lookup$pft[i] = "grass_herb" # forb/herb, subshrub - grass_herb?
    taxon_pft_lookup$commonName[i] = "desert zinnia"}
